Interactive effects of drought and habitat fragmentation on vital rates of an understory tropical plant

### 2021-01-13 analysis/paper/paper.Rmd
implement tredennick year by size GLMM strategy.

One limitation of the DLNM approach is that it does not currently allow for modeling of interactions with a crossbasis function. This limitation meant that we were unable to model a potential size by environment (i.e. drought history) interaction, which may occur with many plant species [@tredennickSizebyenvironmentInteractionsNeglected2018]. To check for a size by environment interaction, we followed the methods of Tredennick et al. [-@tredennickSizebyenvironmentInteractionsNeglected2018] and fit a pair of generalized linear mixed effects models (GLMMs) for each vital rate using the *lme4* package <!--# cite lme4 -->. Rather than explicitly modeling the effects of drought history, we modeled environmental stochasticity with random effects of year. For each vital rate, we included an additional random effect of year on either the intercept or both the intercept and slope of the relationship between plant size and the response. We tested the significance of the year by size interaction with a permutation <!--# not quite permutation, I think?  Check trednnick et al. again for what they call it --> test, again following Treddnick et al. [-@tredennickSizebyenvironmentInteractionsNeglected2018].

@@

>>>>

One limitation of the DLNM approach is that it does not currently allow for modeling of interactions with a crossbasis function. This limitation meant that we were unable to model a potential size by environment (i.e. drought history) interaction, which may occur with many plant species [@tredennickSizebyenvironmentInteractionsNeglected2018]. To check for a size by environment interaction, we followed the methods of Tredennick et al. [-@tredennickSizebyenvironmentInteractionsNeglected2018] and fit a pair of generalized linear mixed effects models (GLMMs) for each vital rate using the *lme4* package <!--# cite lme4 -->. Rather than explicitly modeling the effects of drought history, we modeled environmental stochasticity with random effects of year. For each vital rate, we included an additional random effect of year on either the intercept or both the intercept and slope of the relationship between plant size and the response. We assessed the significance of the year-by-size interaction by testing the likelihood ratio of models with and without the interaction against an expected likelihood ratio distribution under the null hypothesis of no interaction [@tredennickSizebyenvironmentInteractionsNeglected2018].

@@

## Size by year interaction

In continuous forest plots there was support for size by year interactions for growth (95% LR~null~ = 4.54, LR~obs~ = 45.69) and survival (95% LR~null~ = 3.91, LR~obs~ = 29.18) , but not for flowering (95% LR~null~ = 4.44, LR~obs~ = 1.77). However, in 1 ha fragments, we saw no evidence of size by year interaction. For growth 95% LR~null~ = 4.45, LR~obs~ = 4.35, for survival 95% LR~null~ = 4.47, LR~obs~ = 0.62, and for flowering probability 95% LR~null~ = 3.86, LR~obs~ = 2.82. This is consistent with the DLNMs in that the crossbasis functions for \_\_\_ and \_\_\_ were much flatter in fragments compared to continuous forest.
